---
  output: github_document
---

```{r, include=FALSE}
if (requireNamespace("git2r")) {
  repo = git2r::repository(".")
  url = git2r::remote_url(repo, remote = "origin") 
  gh_user = basename(dirname(url))
} else {
  gh_user = "muschellij2"
}
```

[![Travis build status](https://travis-ci.com/`r gh_user`/transcriptr.svg?branch=master)](https://travis-ci.com/`r gh_user`/transcriptr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/`r gh_user`/transcriptr?branch=master&svg=true)](https://ci.appveyor.com/project/`r gh_user`/transcriptr)
[![Coverage status](https://codecov.io/gh/`r gh_user`/transcriptr/branch/master/graph/badge.svg)](https://codecov.io/gh/`r gh_user`/transcriptr)
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# transcriptr Package: 
The goal of `transcriptr` is to provide intends to give the ability to read structured
    PDF files into data available for analysis and tabulation.  Currently
    working for Johns Hopkins Transcripts

## Installation

You can install `transcriptr` from GitHub with:

```
# install.packages("remotes")
remotes::install_github("`r gh_user`/transcriptr")
```

## JHU Transcripts

For the necessary input, please visit https://sis.jhu.edu/sswf/, log in and then go to Registration → My Grades, then click [View Unofficial Transcript].  This should download a `Transcript.pdf`.  The `read_jhu_transcript` will read this in and give a `data.frame` of the parsed output.  

The Shiny app: https://jhubiostatistics.shinyapps.io/validate_curriculum/ should also do this for you, allowing you to download a CSV of your data.  If you want the grades, you must check that box for the export.
